The imprint of global magma oceans on exoplanet demographics

### 2022-11-30 src/tex/ms.tex
define sample selections

    ...long-term goal/overarching objective: derive the geophysical history of rocky extrasolar planets. More concrete: Constrain the limits of runaway greenhouse transitions, and thus the inner edges of the habitable zone. Also: How close is Earth from this runaway greenhouse limit?
   ...
\todo[inline]{introduce magma oceans and their influence on planetary radii~\citep{Dorn2021}.}
    ...current/future observations of planets that are currently in the runaway greenhouse phase may constrain properties of their planetary mantles... make connection between interior and atmospheres.
\end{note}

@@

...

To assign masses to our planets, we use the theoretical mass-radius relationship derived in \citet{Zeng2016}.
The default relation our planets follow is one assuming a pure $\mathrm{MgSiO_3}$ composition.
\todo[inline]{JUSTIFY this choice}
This represents the baseline bulk density before any magma ocean-related effects are applied.
...

\subsubsection{Sample selection}
\begin{note}
    ...
    In this study, we consider only rocky planets with masses \SIrange{0.1}{2}{\Mearth}. % (Turbet+2020 covers only 0.1 to 2 Mearth)
    As we are interested in the effects of runaway greenhouse phases of planets with volatiles and atmosphere, we further excluded lava worlds with extremely high instellation that does not allow long-term preservation of an atmosphere.
    We thus removed all planets with an instellation $S > \SI{2000}{\watt\per\square\meter}$.
\end{note}

>>>>

    ...long-term goal/overarching objective: derive the geophysical history of rocky extrasolar planets. More concrete: Constrain the limits of runaway greenhouse transitions, and thus the inner edges of the habitable zone. Also: How close is Earth from this runaway greenhouse irradiation limit?
   ...
\todo[inline]{introduce magma oceans and their influence on planetary radii~\citep{Dorn2021}.}
    ...current/future observations of planets that are currently in the runaway greenhouse phase may constrain properties of their planetary mantles... make connection between interior and atmospheres.
\end{note}

@@

To assign masses to our planets, we use the semi-empirical mass-radius relationship derived in \citet{Zeng2016}.
The default relation our planets follow is one assuming a pure $\mathrm{MgSiO_3}$ composition.
\todo[inline]{JUSTIFY this choice (TIM?)}
This represents the baseline bulk density before any magma ocean-related effects are applied.

\subsubsection{Sample selection}
\begin{note}
    \todo[inline]{use criterion of Zahnle \& Caitling 2017 instead? $0.8 S^{0.25} < R$}
    The runaway greenhouse effect becomes obsolete where no atmosphere can be maintained due to proximity to the host star and resulting atmospheric erosion.
    We thus excluded planets with extremely high instellation that does not allow long-term preservation of an atmosphere and clear our sample from all planets with an instellation $S > \SI{2000}{\watt\per\square\meter}$.
    We further consider only rocky planets with masses below \SI{2}{\Mearth}. % (Turbet+2020 covers only 0.1 to 2 Mearth)
\end{note}
